\documentclass{article}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.5in]{geometry}

\titleformat{\section}
{\large\bfseries\uppercase}
{}{0em}{}[\titlerule]

\titleformat{\subsection}
{\bfseries\uppercase}
{}{0em}{}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}

\vspace{.25em}
stevesmodish@gmail.com --- stevesmodish.com --- linkedin.com/in/stevesmodish --- github.com/ssmodish

\end{center}
}

\begin{document}

\title{R\'esum\'e}
\author{Steve Smodish}

\maketitle

\section{Summary}
Software Engineer
Full Stack Developer



\section{Education}
\subsection{Lambda School}
\subsubsection{Full Stack Web Development 2019}
Utilized git workflow on all projects.
Completed coursework covering: React, Redux, Node, Express, Less, SQL, Python, C, Data Structures, and Algorithms.
Wrote production-ready code using ReactJS, Redux, and CSS on the frontend and NodeJS and Express on the backend to build single page applications.

\subsection{Florida Atlantic University}
\subsubsection{B.S. General Studies 2016}

\subsection{Palm Beach State College}
\subsubsection{A.S. Internet Services Technology 2015}
\subsubsection{C.C.C. Web Development Specialist 2015}
\subsubsection{C.C.C. Information Technology Administration 2015}
\subsubsection{C.C.C. Cisco Certified Entry Networ Technician (CCENT) 2015}
\subsubsection{C.C.C. Computer Programming Specialist 2016}
\subsubsection{C.C.C. Programming 2016}

\subsection{Full Sail Center for the Recording Arts}
\subsubsection{S.A.D. Recording Engineering 1995}



\section{Employment}
\subsection{Lambda School --- Lambda X Team Leader}
\subsubsection{December 2019 to Present}
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

\subsection{Lambda School --- CS17 Project Manager}
\subsubsection{April 2019 to July 2019}
Conduct daily stand-up meetings with student developers to make sure they understand the algorithm or data structure being presented
Perform daily code reviews to help improve code style as well as reinforce understanding of given topics
Monitor relevant Slack channels for developers asking for help and respond to the best of my ability

\subsection{Self Employed --- Multimedia Producer}
\subsubsection{2000 to Present}
Prepare for upcoming sessions by consulting with clients to get their expectations on paper.
Adapt to new environments, equipment, and team members for every project.
Build upon relationships created during projects to ensure future business.

\subsection{Echo Beach Studios --- Head Engineer}
\subsubsection{1995 to 2013}
Created budgets for hundreds of projects based on exhaustive interviews with potential clients.
Arranged to have the proper equipment and personnel present for productions when necessary.
Troubleshot  equipment issues and made the decision to repair or replace based on the necessities of the production.
Some high profile clients/shows included: Olivia Newton-John, Celine Dion, Snoop Dogg, Clarence Clemons, Burt Reynolds, Venus Williams, Serena Williams, Ahmad Rashad, "Jungle" Jack Hannah, Archer, Aqua Teen Hunger Force, X-Files, Apple, Denny's.




\section{Skills}
\subsection{Languages}
JavaScript, Java, C, C++, C\#, Visual Basic, Python, PHP

\subsection{Frameworks/Libraries}
Express, Knex, React, Vue, Redux, MaterialUI, Bootstrap

\subsection{Classes}
Server Side (PHP) Programming, Java Programming, Visual Basic Programming, Data Structures (SQL), Web Site Administration, Unix/Linux Administration, Discrete Mathematics, Data Structures and Algorithm Analysis



\section{Projects}
\subsection{Flytelog}
\subsubsection{https://lab9-flightlogs.firebaseapp.com/}
Flytelog is an app created to replace/enhance a pilot's logbook.

Created by 6 people over the course of 5 weeks.
Tech stack includes React, MaterialUI, Express, Knex, Firebase OAuth, Firebase Store, Stripe, AWS MySQL.
Travis CI was used to test and deploy the front end to Firebase and Heroku to deploy the back end.
Primary contributions were to DevOps and styling related coding.

\subsection{mystuff}
\subsubsection{https://lambda-build-week-2-use-my-tech-stuff.github.io/marketing/}

Created by 7 people over 4 days.
Tech stack includes CSS Grid, LESS, React, MaterialUI, Express, Mongo Atlas DB
I acted as team leader on this project.
Conducted multiple daily stand-up meetings to facilitate communication between teams.
Performed initial dev-ops setups and, when necessary, trained students to maintain deployments.



\section{Awards}
\subsection{Salutatorian}
\subsubsection{Full Sail Center for the Recording Arts}

\subsection{Course Directors Award: Sound Reinforcement}
\subsubsection{Full Sail Center for the Recording Arts}



\section{Volunteering}
\subsection{Miami Area Meetup Coordinator}
\subsubsection{Lambda School --- May 2019 to Present}
Arrange monthly meetings of students, alumni, and staff members from the Miami area as well as semi-yearly meetups for the state of Florida.
File paperwork necessary to receive payments for meetups.


\subsection{Webmaster}
\subsubsection{Fort Lauderdale SIGGRAPH Professional Chapter --- 2016 to Present}
Guide administrative members in posting activities.
Create, migrate, and maintain sites and services necessary for the organization.




\end{document}